---
title: "Thesis1-TwoSampleCRMvsMBM Framework-Simu2"
author: "Jianing Wang"
date: "11/15/2021"
output: github_document
---

```{r setup, include=FALSE}
## Golbal setting for the entire Markdown
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, error = FALSE)
```

Setup fixed factors
```{r}
nsim <- 1000
targetN <- 5000
targetppl<- seq(1,targetN)
```

# Simulation (framework illustration)

## Goal

I proposed a framework for MBM and CRM to illustrate the underlying sampling mechanism for two methods. One is seen as a process of negative binomial model, while another one is seen as a process of binomial model. Thus, the data generating mechanism for two methods may different. In this set of simulation, some exercises are done to compare NB process for MBM to LP estimator.

## Parameters in MBM

1. $N$: Total population size
2. $p_{B}$: Underlying probability of sampling into the benchmark, draw this once and then fixed, Benchmark population do NOT involve into the simulation as a varying component
3. $p_{2}$: Underlying probability of sampling into the source for multiplier in MBM

## Parameers in CRM

1. $N$: Total population size
2. $p_{1}$: Underlying probability of sampling into sample 1
3. $p_{2}$: Underlying probability of sampling into sample 2

## Scenarios

### Scenario 1.1: Label people with Benchmark, then fixed; only varying p2 for MBM, whereas CRM has two random samples

To mimic the proposed MBM sampling process:

Step 1: Label benchmark people with $p_{B}$ ($p_{B}$ is very small), fixed benchmark are these people exactly across all simulations, the size is call "$n_{B}$". $p_{B} = 0.1$.

Step 2: Start from this step, each iteration of simulation may change the samples. Draw second random sample 2 with $p_{2}$, the size is called "$n_{2}$". $p_{2} = (0.05, 0.1, 0.3, 0.6)$, for each $p_{2}$ value, compute the mean/median/sd of $\hat{N}$, and MSE of $\hat{N}$. Look at the distribution of $\hat{N}$.

Step 3: Given a drawn sample 2, compute number of overlap m and multiplier $p_{m}$, assuming no mismatching or error linkage. $p_{m}$ is a plug-in estimate of $p_{B}$.

Step 4: Compute $\hat{N}$ assuming it follows Negative Binomial distribution: option 1 MLE of $\hat{N} = \frac{n_{B}}{p_{m}}$, this is a biased estimator; option 2 MVUE of $\hat{N} = \frac{n_{B}-1}{p_{m} + 1}$.

To mimic the proposed CRM sampling process:

Step 1: Start from this step, each iteration of simulation may change the samples. Draw second random sample 1 with $p_{1}$, the size is called "$n_{1}$". $p_{1} = (0.05, 0.1, 0.3, 0.6)$.

Step 2: Draw second random sample 2 with $p_{2}$, the size is called "$n_{2}$". $p_{2} = (0.05, 0.1, 0.3, 0.6)$.

Step 3: Use LP estimator and Chapman estimator to compute $\hat{N}$.

Step 4: For each combination of $p_{1}$ and $p_{2}$, compute the Mean/Median/SD of $\hat{N}$, and MSE of $\hat{N}$.

```{r}
# CRM
p1.vec <- c(0.05, 0.1, 0.3, 0.6)
p2.vec <- c(0.05, 0.1, 0.3, 0.6)
scenarios1 <- expand.grid(p2 = p2.vec, p1 = p1.vec)
scenarios1 <- scenarios1[, c("p1","p2")]
# Function to simulate CRM process
source("Simu1.Scenarios.Functions.R")
# Run simulation, get summary statistics for CRM process
simu2.crm.1.Nhat <- crm.1.ls(simsize = nsim, pplsize = targetN, p1 = scenarios1$p1, p2 = scenarios1$p2)
```

```{r}
# MBM
pB.vec <- c(0.05, 0.1, 0.3, 0.6)
p2.vec <- c(0.05, 0.1, 0.3, 0.6)
scenarios1 <- expand.grid(p2 = p2.vec, pB = pB.vec)
scenarios1 <- scenarios1[, c("pB","p2")]
# Function to simulate MBM process
source("Simu1.Scenarios.Functions.R")
# Run simulation, get summary statistics for MBM process
simu2.mbm.1.Nhat <- mbm.1.ls(simsize = nsim, pplsize = targetN, pB = scenarios1$pB, p2 = scenarios1$p2)
```

Plots for each value of $p_{1}$ ($p_{B}$), compare the relative bias with 95\% confidencen interval areas between the framework of CRM and MBM.

```{r}
# Plot 1
# Compare CRM LP & Chapman vs MBM NB & Direct
source("Simu1.Scenarios.Functions.R")
simu2.plot.CRM.MBM.diff.Est(dt.crm = simu2.crm.1.Nhat, dt.mbm = simu2.mbm.1.Nhat, p1_pB = p1.vec[1], title = "(A)")
simu2.plot.CRM.MBM.diff.Est(dt.crm = simu2.crm.1.Nhat, dt.mbm = simu2.mbm.1.Nhat, p1_pB = p1.vec[2], title = "(B)")
simu2.plot.CRM.MBM.diff.Est(dt.crm = simu2.crm.1.Nhat, dt.mbm = simu2.mbm.1.Nhat, p1_pB = p1.vec[3], title = "(C)")
simu2.plot.CRM.MBM.diff.Est(dt.crm = simu2.crm.1.Nhat, dt.mbm = simu2.mbm.1.Nhat, p1_pB = p1.vec[4], title = "(D)")
```

### Understand the source of bias of estimators

To understand why neither MLE nor MVUE could work for MBM, we investigate if the estimate of $p_{2}$ using $\hat{p}_{1}$ is biased, because essentially this is a two-stage estimation, the first is using $\hat{p}_{1}$ to estimate $p_{2}$, and then plug this estimate into a model for $N$ estimation. If the estimate of $p_{2}$ is biased, even we choose a good estimator for $N$, the result keeps biased due to a bias when estimating $p_{2}$.

Plot $p_{2}$ vs $\hat{p}_{1}$ to see if $\hat{p}_{1}$ is not doing well in estimating $p_{2}$.

```{r}
# Plot 2
# Compare CRM vs MBM on plug-in estimate p_m
source("Simu1.Scenarios.Functions.R")
simu2.plot.CRM.MBM.diff.p_m(dt.crm = simu2.crm.1.Nhat, dt.mbm = simu2.mbm.1.Nhat, p1_pB = p1.vec[1], title = "(A)")
simu2.plot.CRM.MBM.diff.p_m(dt.crm = simu2.crm.1.Nhat, dt.mbm = simu2.mbm.1.Nhat, p1_pB = p1.vec[2], title = "(B)")
simu2.plot.CRM.MBM.diff.p_m(dt.crm = simu2.crm.1.Nhat, dt.mbm = simu2.mbm.1.Nhat, p1_pB = p1.vec[3], title = "(C)")
simu2.plot.CRM.MBM.diff.p_m(dt.crm = simu2.crm.1.Nhat, dt.mbm = simu2.mbm.1.Nhat, p1_pB = p1.vec[4], title = "(D)")
```

