---
title: "Thesis1-TwoSampleCRMvsMBM Framework-Simu2"
author: "Jianing Wang"
date: "11/15/2021"
output: github_document
---

```{r setup, include=FALSE}
## Golbal setting for the entire Markdown
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, error = FALSE)
```

Setup fixed factors
```{r}
nsim <- 1000
targetN <- 5000
targetppl<- seq(1,targetN)
```

# Simulation set 2

## Goal
I proposed a framework for MBM and CRM to illustrate the underlying sampling mechanism for two methods. One is seen as a process of negative binomial model, while another one is seen as a process of binomial model. Thus, the data generating mechanism for two methods may different. In this set of simulation, some exercises are done to compare NB process for MBM to LP estimator

## Parameters in MBM
N: Total population size
pB: Underlying probability of sampling into the benchmark, draw this once and then fixed, Benchmark population do NOT involve into the simulation as a varying component
p2: Underlying probability of sampling into the source for multiplier in MBM

## Parameers in CRM
N: Total population size
p1: Underlying probability of sampling into sample 1
p2: Underlying probability of sampling into sample 2

## Scenarios
### Scenario 1.1: Label people with Benchmark, then fixed; only varying p2 for MBM, whereas CRM has two random samples
To mimic the proposed MBM sampling process
Step 1: Label benchmark people with pB (pB is very small), fixed benchmark are these people exactly across all simulations, the size is call "nB". pB = 0.1
Step 2: Start from this step, each iteration of simulation may change the samples. Draw second random sample 2 with p2, the size is called "n2". p2 = c(0.05, 0.1, 0.3, 0.6), for each p2 value, compute the mean/median/sd of Nhat, and MSE of Nhat. Look at the distribution of Nhat
Step 3: Given a drawn sample 2, compute number of overlap m and multiplier p_m, assuming no mismatching or error linkage. p_m is a plug-in estimate of pB
Step 4: Compute Nhat assuming it follows NB distribution: option 1 MLE of Nhat = nB/p_m, this is a biased estimator; option 2 MVUE of Nhat = (nB-1)/p_m + 1

To mimic the proposed CRM sampling process
Step 1: Start from this step, each iteration of simulation may change the samples. Draw second random sample 1 with p1, the size is called "n1". p1 = c(0.05, 0.1, 0.3, 0.6)
Step 2: Draw second random sample 2 with p2, the size is called "n2". p2 = c(0.05, 0.1, 0.3, 0.6)
Step 3: Use LP estimator and Chapman estimator to compute Nhat
LP estimator = n1* n2/m; Chapman estimator = (n1+1)*(n2+1)/(m+1) - 1
Step 4: For each combination of p1 and p2, compute the mean/median/sd of Nhat, and MSE of Nhat. Look at the distribution of Nhat

Results:
The simulation results should demonstrate the mean/median/SD/min/max/MSE of Nhat, and true/mean/median/min/max of overlap counts, as well as the one-sample t-test.

```{r}
# Scenario 1 for CRM
p1.vec <- c(0.05, 0.1, 0.3, 0.6)
p2.vec <- c(0.05, 0.1, 0.3, 0.6)
scenarios1 <- expand.grid(p2 = p2.vec, p1 = p1.vec)
scenarios1 <- scenarios1[, c("p1","p2")]
# Function to simulate CRM process
source("Simu2.Scenarios.Functions.R")
# Run simulation, get summary statistics for CRM process
simu2.crm.1.Nhat <- crm.1.ls(simsize = nsim, pplsize = targetN, p1 = scenarios1$p1, p2 = scenarios1$p2)
write.csv(simu2.crm.1.Nhat, file = "/Users/jianingwang/Documents/Boston U PhD/___My Dissertation___/Work2_IndirectEst/_ThesisWork1-TwoSampleMBMvsCRM/Work1-Simulation/Simulation Framework/Outputs/ResultTb/simu2.crm.1.Nhat.csv", row.names = FALSE)
```

```{r}
# Scenario 1 for MBM
pB.vec <- c(0.05, 0.1, 0.3, 0.6)
p2.vec <- c(0.05, 0.1, 0.3, 0.6)
scenarios1 <- expand.grid(p2 = p2.vec, pB = pB.vec)
scenarios1 <- scenarios1[, c("pB","p2")]
# Function to simulate CRM process
source("Simu2.Scenarios.Functions.R")
# Run simulation, get summary statistics for CRM process
simu2.mbm.1.Nhat <- mbm.1.ls(simsize = nsim, pplsize = targetN, pB = scenarios1$pB, p2 = scenarios1$p2)
# Save the output
write.csv(simu2.mbm.1.Nhat, file = "/Users/jianingwang/Documents/Boston U PhD/___My Dissertation___/Work2_IndirectEst/_ThesisWork1-TwoSampleMBMvsCRM/Work1-Simulation/Simulation Framework/Outputs/ResultTb/simu2.mbm.1.Nhat.csv", row.names = FALSE)
```

Plots for each value of p1 (pB), compare the relative bias with LB95/UB95 areas between the framework of CRM and MBM
```{r}
# Plot 1
# Compare CRM LP & Chapman vs MBM NB & Direct
source("Simu2.Scenarios.Functions.R")
simu2.plot.CRM.MBM.diff.Est(dt.crm = simu2.crm.1.Nhat, dt.mbm = simu2.mbm.1.Nhat, p1_pB = p1.vec[1])
simu2.plot.CRM.MBM.diff.Est(dt.crm = simu2.crm.1.Nhat, dt.mbm = simu2.mbm.1.Nhat, p1_pB = p1.vec[2])
simu2.plot.CRM.MBM.diff.Est(dt.crm = simu2.crm.1.Nhat, dt.mbm = simu2.mbm.1.Nhat, p1_pB = p1.vec[3])
simu2.plot.CRM.MBM.diff.Est(dt.crm = simu2.crm.1.Nhat, dt.mbm = simu2.mbm.1.Nhat, p1_pB = p1.vec[4])
```
Findings:
P-values from one-sample t-test (two-sided, greater, and less) should give some sense on how does the estimator would bias.

Fundamental proof in theory via jensen's inequality is proved that LP estimator is MLE but biased and tends to overestimate.

To understand why neither MLE nor MVUE could work for MBM, we investigate if the estimate of p2 using p_m is biased, because essentially this is a two-stage estimation, the first is using p_m to estimate p2, and then plug this estimate into a model for N estimation. If the estimate of p2 is biased, even we choose a good estimator for N, the result keeps biased due to a bias when estimating p2.

Plot p2 vs p_m to see if p_m is not doing well in estimating p2.
```{r}
# Plot 2
# Compare CRM vs MBM on plug-in estimate p_m
source("Simu2.Scenarios.Functions.R")
simu2.plot.CRM.MBM.diff.p_m(dt.crm = simu2.crm.1.Nhat, dt.mbm = simu2.mbm.1.Nhat, p1_pB = p1.vec[1])
simu2.plot.CRM.MBM.diff.p_m(dt.crm = simu2.crm.1.Nhat, dt.mbm = simu2.mbm.1.Nhat, p1_pB = p1.vec[2])
simu2.plot.CRM.MBM.diff.p_m(dt.crm = simu2.crm.1.Nhat, dt.mbm = simu2.mbm.1.Nhat, p1_pB = p1.vec[3])
simu2.plot.CRM.MBM.diff.p_m(dt.crm = simu2.crm.1.Nhat, dt.mbm = simu2.mbm.1.Nhat, p1_pB = p1.vec[4])
```

??? Why it cannot give me the same answer??
```{r}
simu2.mbm.1.Nhat <- read.csv("/Users/jianingwang/Documents/Boston U PhD/___My Dissertation___/Work2_IndirectEst/_ThesisWork1-TwoSampleMBMvsCRM/Work1-Simulation/Simulation Framework/Outputs/ResultTb/GoldStandard/simu2.mbm.1.Nhat.csv")
source("Simu2.Scenarios.Functions.R")
simu2.plot.CRM.MBM.diff.p_m(dt.crm = simu2.crm.1.Nhat, dt.mbm = simu2.mbm.1.Nhat, p1_pB = p1.vec[1])
simu2.plot.CRM.MBM.diff.p_m(dt.crm = simu2.crm.1.Nhat, dt.mbm = simu2.mbm.1.Nhat, p1_pB = p1.vec[2])
simu2.plot.CRM.MBM.diff.p_m(dt.crm = simu2.crm.1.Nhat, dt.mbm = simu2.mbm.1.Nhat, p1_pB = p1.vec[3])
simu2.plot.CRM.MBM.diff.p_m(dt.crm = simu2.crm.1.Nhat, dt.mbm = simu2.mbm.1.Nhat, p1_pB = p1.vec[4])

```




We also wonder if the coverage of the sample 1 and sample 2 has an impact. From the current plot we can see that the bias is higher in the case with sample 1 (benchmark) being low coverage than being higher coverage. The bias is also higher when p2 is small.

We compare if the relative coverage has an impact too. So we first compute the relative coverage by dividing the p1(pB) by p2.

```{r}
simu2.crm.1.Nhat$rel.p1.to.p2 <- round(simu2.crm.1.Nhat$p1/simu2.crm.1.Nhat$p2,digits = 3)
simu2.mbm.1.Nhat$rel.pB.to.p2 <- round(simu2.mbm.1.Nhat$pB/simu2.mbm.1.Nhat$p2,digits = 3)
```

Plot
```{r}
source("Simu2.Scenarios.Functions.R")
simu2.plot.CRM.MBM.p1.to.p2(dt.crm = simu2.crm.1.Nhat, dt.mbm = simu2.mbm.1.Nhat)
```

This plot shows that when one source has much larger coverage than another, the estimators perform well. When two sources have similar coverage but both low coverage, then the estimators perform bad. LP is more biased, followed by two MBM estimator. The Chapman estimator always performs well.

